Model_CFU

### 2016-12-16 Projects/HumanCdGF_cdiff_colonization.Rmd
fix label for plot with leaving 581 out

@@

set.seed(seed)
cfu_wo581_rf <- randomForest(cfu_wo581_df[ , -2], cfu_wo581_df$log_cfu_med,
                           ntree = 1001,
                           mtry = 15,
                           importance = T)
top_features_wo581 <- head(sort(importance(cfu_wo581_rf)[,1],decreasing = T), n_features)
```

@@

>>>>

#### Model __Colonization level__ with Human Donor included (without Donor 581):

@@

set.seed(seed)
cfu_wo581_rf <- randomForest(cfu_wo581_df[ , -2], cfu_wo581_df$log_cfu_med,
                           ntree = 1001,
                           mtry = 15,
                           importance = T)
top_features_wo581 <- head(sort(importance(cfu_wo581_rf)[,1],decreasing = T), n_features)

cfu_ACD_df <- colonized_cfu %>% 
    select(mouse_id, human_source, cage_id, log_cfu_med) %>% 
    right_join(community_all_d0) %>% 
    select(-mouse_id) %>% 
    filter(!is.na(log_cfu_med))
cfu_ACD_df$human_source <- factor(cfu_ACD_df$human_source)

cfu_single581_df <- filter(cfu_ACD_df, !cage_id %in% c('A','C')) %>% 
                      select(-cage_id)
set.seed(seed)
cfu_D_rf <- randomForest(cfu_single581_df[ , -2], cfu_single581_df$log_cfu_med,
                           ntree = 1001,
                           mtry = 15,
                           importance = T)
cfu_single581_df <- filter(cfu_ACD_df, !cage_id %in% c('A','D')) %>% 
                      select(-cage_id)
set.seed(seed)
cfu_C_rf <- randomForest(cfu_single581_df[ , -2], cfu_single581_df$log_cfu_med,
                           ntree = 1001,
                           mtry = 15,
                           importance = T)
cfu_single581_df <- filter(cfu_ACD_df, !cage_id %in% c('D','C')) %>% 
                      select(-cage_id)
set.seed(seed)
cfu_A_rf <- randomForest(cfu_single581_df[ , -2], cfu_single581_df$log_cfu_med,
                           ntree = 1001,
                           mtry = 15,
                           importance = T)
```

@@

Including one Donor 581 cage increases performance:  
w/Cage A: `r paste0(round(tail(cfu_A_rf$rsq, 1), 4)*100, '% Var Explained')`   
w/Cage C: `r paste0(round(tail(cfu_C_rf$rsq, 1), 4)*100, '% Var Explained')`   
w/Cage D: `r paste0(round(tail(cfu_D_rf$rsq, 1), 4)*100, '% Var Explained')`
